Reaching is Better When You Get What You Want: Realtime Feedback of Intended Reaching Trajectory Despite an Unstable Environment

### 2015-05-27 Paper2frontiers/frontiers.tex
getting closer

Specific planned state trajectory even in the absence of explicit kinematic constraints.

Of particular scientific interest, "strict invariant" which has been described as opposite optimal feedback control.

Stiffness decreased, which provides secondary evidence of lower instability and unpredictability. Well, maybe it's just because of the numbers we chose. If we crank them down, can we get the stiffness even lower? Not so much. So clearly getting the stiffness right is very important.
In the absence of disturbing forces, estimated intent accuracy was lower than
that of the hand, which suggests the need for model improvements.

 The simplest explanation for this is that IF approximates a signal already known to the brain: the path planned for the hand. If so, IF r Moreover, this immediate performance enhancement during human-machine interaction implies a means by which robots can productively interact with a human without impeding them.

While this is pretty awesome, getting the stiffness right is an enormous limitation. Moreover, the stiffness model breaks down in the vicinity of the target for reasons unknown. The nature of control might be changing there and if so, we don't really know the specifics, but Shapiro has something to say about this.

Overall, this is something of a breakthrough

>>>>

The ease with which subjects could make use of their estimated intent provides strong preliminary evidence that a specific desired state trajectory is computed even when moving in a highly variable environment. While the nature of the force disturbance and its high trial-to-trial variability prevent clear characterization of learning, subjects appear to have learned to use their intent within the first exposure. While recent work has identified kinematic constraints irrelevant to the task \citep{mistry2013optimal}, this is the first direct evidence that the entire trajectory is controlled even in the absence of specific instructions or constraints. It remains unclear when the intended trajectory is computed, but variability in the desired trajectory in phases 2 and 4 suggests that the trajectory is planed or at least can be replanned mid-movement. Certainly, it is not finalized before the onset of movement and is not a "strict invariant." Intent determination provides us with a novel and useful window into the nature of motor control.

IF can facilitate human-machine collaboration and artificial performance augmentation by enabling the machine to preserve an operators intent while cancelling unexpected disturbanes from the environment. This would reduce the demands on the human operator increase performance, especially in environments with rapidly changing conditions that can be quickly and accurately measured with electronic instrumentation. This assistance goes beyond environment cancellation by also accounting for any corrections the operator might make based on their expectation of disturbance.

Limitatinos. The stiffness model is shit-tastic. Reaching trajectories, but not tracking, nonlinear, or 3D.

The general intent extraction approach presented here reveals the conditions needed to solve for the moving intent in an arbitrary dynamic process. Sensitivity analysis for this approach applied to the human arm demonstrated favorable conditions for determination of intent during force-disturbed reaching. Reaching intent became significantly different from baseline reaching only after enough time had elapsed for the disturbance to be processed and descending motor commands to change. This window into intent should allow advances in arm modeling, motor training, and human-machine interaction.
